\LARGE \bf Stochastic Uncertainty Propagation in Power System Dynamics using Measure-valued Proximal Recursions

### 2021-06-24 Papers/Stochastic_Uncertainty_Propagation_TPS/JKO_Power_Systems_TPS.tex
updating Section V

Finally, we transform the proximal updates back to the $\left(\bm{\theta},\bm{\omega}\right)^{\top}$ state space via the pushforward $\bm{\Psi}^{-1}$ as
\begin{align}
\varrho_{k}\left(\bm{\theta}_{k}^{i},\bm{\omega}_{k}^{i}\right) &= \bm{\Psi}^{-1}_{\sharp} \tilde{\varrho}_{k}\left(\bm{\xi}_{k}^{i},\bm{\eta}_{k}^{i}\right) \nonumber\\
&= \left(\prod_{j=1}^{n}m_{j}/\sigma_{j}\right)^{\!\!2}\tilde{\varrho}_{k}\left(\bm{M}\bm{\Sigma}^{-1}\bm{\theta}_{k}^{i},\bm{M}\bm{\Sigma}^{-1}\bm{\omega}_{k}^{i}\right),
\label{BringBackOriginalStateSpace}	
\end{align}
for all $i=1,\hdots,N$. The $\varrho_{k}\left(\bm{\theta},\bm{\omega}\right)$ from \eqref{BringBackOriginalStateSpace} approximates $\rho(t,\bm{\theta},\bm{\omega})$ (the transient solution of \eqref{KineticFPK}) in the sense \eqref{ConvergenceGuarantee}.

@@

\begin{table}[t]
\centering
\begin{tabular}{| l | l |} 
\hline
Parameter description & Values\\
\hline\hline
&\\
frequency & $f_{0} = 60$ Hz\\
&\\
inertia & $m_{i}\in{\rm{Unif}}\left([2,12]\right)/2\pi f_{0}$\\
& \\
damping coefficient & $\gamma_{i}\in{\rm{Unif}}\left([20,30]\right)/2\pi f_{0}$\\
& \\
diffusion coefficient & $\sigma_{i}\in{\rm{Unif}}\left([1,5]\right)$\\
& \\
tangent of phase shift & $\tan\varphi_{ij}\in{\rm{Unif}}\left([0,0.25]\right)$\\
& \\
effective power input & $P_{i}\in{\rm{Unif}}\left([0,10]\right)$\\
& \\
coupling coefficient & $k_{ij}\begin{cases}
=0 & \text{for}\; i=j,\\
\in{\rm{Unif}}\left([0.7,1.2]\right) & \text{for}\; i\neq j.	
\end{cases}$\\
& \\
\hline
\end{tabular}
\caption{Parameters used for the numerical simulation reported in Sec. \ref{subsec:NumSimSynthetic}. The indices $i,j\in\{1,\hdots,n\}$.}
\label{table:ParamUncertaintiesSynthetic}
\end{table}

\subsection{Synthetic Test System}\label{subsec:NumSimSynthetic}
We consider a power network with $n=20$ generators, and propagate the transient joint state PDFs supported over $\mathbb{T}^{20}\times\mathbb{R}^{20}$. We take the initial joint state PDF at $t=0$ as
\begin{align*}
\rho_{0}\equiv\rho(t=0,\theta(0),\omega(0)) = &\;{\rm{Unif}}\left(\left([0,2\pi)\;\text{rad}\right)^{n}\right)\\
	&\qquad\times {\rm{Unif}}\left([-0.1,0.1]\;\text{rad/s}\right),
\end{align*}
and following \cite[Sec. 5]{dorfler2012synchronization}, randomly generate the parameters as in Table \ref{table:ParamUncertaintiesSynthetic}. These parameter ranges are consistent with the same found in \cite{sauerpai1998,andersonBook1977,kundurBook1994}.

For $N=1000$ random samples

>>>>

Finally, we transform the proximal updates back to the $\left(\bm{\theta},\bm{\omega}\right)^{\top}$ state space via the pushforward $\bm{\Psi}^{-1}$ as
\begin{align}
\varrho_{k}\left(\bm{\theta}_{k}^{i},\bm{\omega}_{k}^{i}\right) &= \bm{\Psi}^{-1}_{\sharp} \tilde{\varrho}_{k}\left(\bm{\xi}_{k}^{i},\bm{\eta}_{k}^{i}\right) \nonumber\\
&= \left(\prod_{j=1}^{n}m_{j}/\sigma_{j}\right)^{\!\!2}\tilde{\varrho}_{k}\left(\bm{M}\bm{\Sigma}^{-1}\bm{\theta}_{k}^{i},\bm{M}\bm{\Sigma}^{-1}\bm{\omega}_{k}^{i}\right),
\label{BringBackOriginalStateSpace}	
\end{align}
for all $i=1,\hdots,N$. The $\varrho_{k}\left(\bm{\theta},\bm{\omega}\right)$ from \eqref{BringBackOriginalStateSpace} approximates $\rho(t,\bm{\theta},\bm{\omega})$ (the transient solution of \eqref{KineticFPK}) in the sense \eqref{ConvergenceGuarantee}. For completeness, the overall algorithm is {\red{given}}.

@@

\begin{table}[t]
\centering
\begin{tabular}{| l | l |} 
\hline
Parameter description & Values\\
\hline\hline
&\\
frequency & $f_{0} = 60$ Hz\\
&\\
inertia & $m_{i}\in{\rm{Unif}}\left([2,12]\right)/2\pi f_{0}$\\
& \\
damping coefficient & $\gamma_{i}\in{\rm{Unif}}\left([20,30]\right)/2\pi f_{0}$\\
& \\
diffusion coefficient & $\sigma_{i}\in{\rm{Unif}}\left([1,5]\right)$\\
& \\
tangent of phase shift & $\tan\varphi_{ij}\begin{cases}
=0 & \text{for}\; i=j\\
\in{\rm{Unif}}\left([0,0.25]\right)& \text{for}\; i\neq j
\end{cases}$\\
& \\
effective power input & $P_{i}\in{\rm{Unif}}\left([0,10]\right)$\\
& \\
coupling coefficient & $k_{ij}\begin{cases}
=0 & \text{for}\; i=j\\
\in{\rm{Unif}}\left([0.7,1.2]\right) & \text{for}\; i\neq j	
\end{cases}$\\
& \\
\hline
\end{tabular}
\caption{Parameters used for the numerical simulation reported in Sec. \ref{subsec:NumSimSynthetic}. The indices $i,j\in\{1,\hdots,n\}$.}
\label{table:ParamUncertaintiesSynthetic}
\end{table}

\subsection{Synthetic Test System}\label{subsec:NumSimSynthetic}
We consider a power network with $n=20$ generators, and propagate the transient joint state PDFs supported over $\mathbb{T}^{20}\times\mathbb{R}^{20}$. We take the initial joint state PDF at $t=0$ as
\begin{align}
\rho_{0}\equiv\rho(t=0,\theta(0),\omega(0)) = &\;{\rm{Unif}}\left(\left([0,2\pi)\;\text{rad}\right)^{n}\right)\\
	&\qquad\times {\rm{Unif}}\left([-0.1,0.1]\;\text{rad/s}\right),
\label{rho0synthetic}	
\end{align}
and following \cite[Sec. 5]{dorfler2012synchronization}, randomly generate the parameters as in Table \ref{table:ParamUncertaintiesSynthetic}. These parameter ranges are consistent with the same found in \cite{sauerpai1998,andersonBook1977,kundurBook1994}.

For $N=1000$ random samples from the initial joint PDF \eqref{rho0synthetic}, we use Algorithm
